### 2016-09-06 FrontBackmatter/Introduction.tex
Save the day's work. Chapter 1 almost done
Minor adjustments to text
Chaps. 1, 2, and 5 are complete

\epigraph{
pity this busy monster, manunkind,
    }{
    --- \textsc{E. E. Cummings}}

\epigraph{
[...] \textnorsk{og fordi jeg alltid har hatt en dragning mot det skjulte og hemmelige.}
}{
--- \textnorsk{\textsc{K. O. Knausgård}, \textit{Om Høsten}}}

@@

\begin{figure}[!h]
\centering
\scalebox{0.8}{\input{gfx/RQC-axes.tikz}}
\caption[Pictorial depiction of the concept of \emph{model chemistries}.]{
Pictorial depiction of the concept of \emph{model chemistries} as the
three dimensions of quantum chemistry.~\autocite{Pople1999-gt, Saue2011-qg}
The computational scaling of a model chemistry is
$S=\textcolor{PMS1797}{y}(\textcolor{PMS2229}{x})f(\textcolor{PMS2229}{x})\textcolor{PMS130}{M}^{\textcolor{PMS2229}{x}}$.
}
\label{fig:RQC-axis}
\end{figure}

@@

\todo[inline]{Classification of solute-solvent interactions. The focus
on electrostatics.}

@@

Faced with the problem of describing such a diverse array of effects,
two main models have emerged in the past decades, each with its
strengths and weaknesses.
Both can be classified as \emph{multiscale} (or \emph{focused})
models~\autocite{Nobel2013} and hinge on the same idea: treat different
parts of the system with different methods and couple these methods by
bridging "scales" at the boundary, \emph{vide infra}.
While both models treat the molecular degrees of freedom at the quantum
mechanical level, their approach to the microscopic description of the
degrees of freedom of the environment differs:
\begin{itemize}
 \item
   \emph{Discrete} (or \emph{explicit}) models explicitly treat those
   degrees of freedom.
   This is either achieved by a cheaper quantum mechanical
   method~\autocite{Vreven2006-gx} or by \gls{MM}.~\autocite{Senn2009-sk}
   In the latter approach, commonly dubbed \acrshort{QM}/\acrshort{MM}, the \acrshort{MM}
   region can either be polarizable~\autocite{MMPol} or non
   polarizable.~\autocite{MM}
 \item
   \emph{Continuum} (or \emph{implicit}) completely remove the degrees
   of freedom of the environment from the picture, replacing it with a
   structureless continuum.
   The effect of this continuum is described, classically, \emph{via}
   its bulk properties.~\autocite{Onsager1936-wf, Miertus1981-mm}
\end{itemize}
\acrshort{QM}/\acrshort{MM} models can capture, albeit approximately, the effect
of the atomistic nature of the environment on the active part of the
system.
However, they demand a statistical average of environment configurations
to yield results of any significance. Moreover, a large number
\emph{cutoff} for the \acrshort{MM} region is usually required to converge
long-range electrostatic interactions.~\autocite{Something here??}
Continuum models avoid both problems at once. Statistical averaging is
built into the model \emph{via} their parametrization by
means of the environment's bulk properties, such as the permittivity.
In addition, long-range electrostatics is treated exactly.
Unfortunately, atomistic detail is lost and it is then impossible to
recover a satisfactory description of specific effects.
To partly alleviate these sources of error, the \acrshort{QM}/\acrshort{MM} and
\acrshort{QM}/Continuum methods can and have been successfully combined to
yield the three-layer \acrshort{QM}/\acrshort{MM}/Continuum method.~\autocite{Curutchet, Steindal Lipparini}
Figure \ref{fig:qm-to-multiscale} schematically portrays the transition
from a full \acrshort{QM} model of the relevant system to its multiscale
representations.

@@

Notice that we have deliberately ruled out so-called \emph{cluster}
models from the above discussion.~\autocite{ClusterModels}
These approaches replace the actual physical setting with a suitable
truncation of the whole solute+solvent system, the \emph{model system}
and treat it within a chosen quantum mechanical level of theory.
Cluster models can be used to benchmark more approximate multiscale
models, but their description is outside the scope of this thesis.

>>>>

\begin{epigraphs}
\qitem{
pity this busy monster, manunkind,
    }{
    --- \textsc{E. E. Cummings}}
\qitem{
[...] \textnorsk{og fordi jeg alltid har hatt en dragning mot det skjulte og hemmelige.}
}{
--- \textnorsk{\textsc{K. O. Knausgård}, \textit{Om Høsten}}}
\end{epigraphs}

@@

\begin{figure}[tb]
\centering
\scalebox{0.7}{\input{gfx/RQC-axes.tikz}}
\caption[Pictorial depiction of the concept of \emph{model chemistries}.]{
Pictorial depiction of the concept of \emph{model chemistries} as the
three dimensions of quantum chemistry.~\autocite{Pople1999-gt, Saue2011-qg}
The computational scaling of a model chemistry is
$S=\textcolor{PMS1797}{y}(\textcolor{PMS2229}{x})f(\textcolor{PMS2229}{x})\textcolor{PMS130}{M}^{\textcolor{PMS2229}{x}}$.
}
\label{fig:RQC-axis}
\end{figure}

@@

@@

Faced with the problem of describing such a diverse array of effects,
two main models have emerged in the past decades, each with its
strengths and weaknesses.
Both can be classified as \emph{multiscale} (or \emph{focused})
models~\autocite{Nobel2013} and hinge on the same idea: treat different
parts of the system with different methods and couple these methods by
bridging "scales" at the boundary, \emph{vide infra}.
While both models treat the molecular degrees of freedom at the quantum
mechanical level, their approach to the microscopic description of the
degrees of freedom of the environment differs:
\begin{itemize}
 \item
   \emph{Discrete} (or \emph{explicit}) models explicitly treat those
   degrees of freedom.
   This is either achieved by a cheaper quantum mechanical
   method~\autocite{Vreven2006-gx} or by \gls{MM}.~\autocite{Senn2009-sk}
   In the latter approach, commonly dubbed \acrshort{QM}/\acrshort{MM}, the \acrshort{MM}
   region can either be polarizable~\autocite{Mennucci2013-go,
   Olsen2010-wa, Lipparini2011-rd} or non
   polarizable. While the former method allows for mutual polarization
   between the \acrshort*{QM} and \acrshort*{MM} subsystems, the latter
   treats the \acrshort*{MM} region as fixed.
 \item
   \emph{Continuum} (or \emph{implicit}) completely remove the degrees
   of freedom of the environment from the picture, replacing it with a
   structureless continuum.
   The effect of this continuum is described, classically, \emph{via}
   its bulk properties.~\autocite{Onsager1936-wf, Miertus1981-mm}
\end{itemize}
\acrshort{QM}/\acrshort{MM} models can capture, albeit approximately, the effect
of the atomistic nature of the environment on the active part of the
system.
However, they demand a statistical average of environment configurations
to yield results of any significance. Moreover, a large number
\emph{cutoff} for the \acrshort{MM} region is usually required to converge
long-range electrostatic interactions.\autocite{Steindal2011-ki}
Continuum models avoid both problems at once. Statistical averaging is
built into the model \emph{via} their parametrization by
means of the environment's bulk properties, such as the permittivity.
In addition, long-range electrostatics is treated exactly.
Unfortunately, atomistic detail is lost and it is then impossible to
recover a satisfactory description of specific effects.
To partly alleviate these sources of error, the
\acrshort{QM}/\acrshort{MM} and \acrshort{QM}/Continuum methods can and
have been successfully combined to yield the three-layer
\acrshort{QM}/\acrshort{MM}/Continuum method.\autocite{Steindal2011-ki,
Lipparini2011-rd, Caprasecca2012-ir, Lipparini2013-ud}
Figure \ref{fig:qm-to-multiscale} schematically portrays the transition
from a full \acrshort{QM} model of the relevant system to its multiscale
representations.

@@

Notice that we have deliberately ruled out so-called \emph{cluster}
models from the above discussion.
These approaches replace the actual physical setting with a suitable
truncation of the whole solute+solvent system, the \emph{model system}
and treat it within a chosen quantum mechanical level of theory.
Cluster models can be used to benchmark more approximate multiscale
models, but their description is outside the scope of this thesis.
